Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-15 paper.qmd
Added pkg dowloads with latest version

if (!requireNamespace("remotes", quietly = TRUE)) {
  install.packages("remotes")
}

@@

if (!requireNamespace("tibble", quietly = TRUE)) {
  install.packages("tibble")
}

if (!requireNamespace("dplyr", quietly = TRUE)) {
  install.packages("dplyr")
}

if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

if (!requireNamespace("readr", quietly = TRUE)) {
  install.packages("readr")
}

if (!requireNamespace("tidyr", quietly = TRUE)) {
  install.packages("tidyr")
}

if (!requireNamespace("patchwork", quietly = TRUE)) {
  install.packages("patchwork")
}

if (!requireNamespace("colorspace", quietly = TRUE)) {
  install.packages("colorspace")
}

if (!requireNamespace("kableExtra", quietly = TRUE)) {
  install.packages("kableExtra")
}

if (!requireNamespace("conflicted", quietly = TRUE)) {
  install.packages("conflicted")
}
```

>>>>

options(repos = c(CRAN = "https://cran.rstudio.com")) # Setup mirror

packages_to_check <- c("remotes", "tibble", "dplyr", "ggplot2", "tidyr", "readr", "patchwork", "colorspace", "kableExtra", "conflicted")

for (pkg in packages_to_check) {
  if (!requireNamespace(pkg, quietly = TRUE)) {
    message(paste("Installing package:", pkg))
    install.packages(pkg)
  } else {
    installed_version <- packageVersion(pkg)
    available_version <- tryCatch({
      utils::packageDescription(pkg)$Version
    }, error = function(e) NA) # Handle cases where package info isn't readily available

    if (!is.na(available_version) && installed_version < package_version(available_version)) {
      message(paste("A newer version of package", pkg, "is available. Updating..."))
      install.packages(pkg)
    } else {
      message(paste("Package", pkg, "is up-to-date (version", installed_version, ")."))
    }
  }
}

@@
